---
title: Innlevering 3
author: Innlevering 3 i Data Science 2021 - Maren Sognefest og Daniel Karstad
Affiliation: HVL
email: 152148@stud.hvl.no & 598289@stud.hvl.no
bibliography: 
bib-humanities: true
nocite: 
lang: no-NB
fontsize: 12pt
linestretch: 1.5
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
  html_notebook: default
---
```{r echo=FALSE}
library(styler) 
library(gapminder)
```
hei test

1. What information does the fileddf_concepts.csv contain?

```{r}
data(ddf_concepts)
```


2. What information does the file ddf--entities--geo--country.csv contain?

3. What information does the file ddf--entities--geo--un_sdg_region.csv contain?

4. What variables does the gapminder dataset from the gapminder package contain? To what continentare Australia and New Zealand assigned?
```{r}
data(gapminder)
```

5. Recreate thecontinentvariable in gapminder with the new data (Hint! Move Australia and NewZealand from Asia to Oceania). Only include countries that have aiso3166_1_alpha3code. Use datafromddf--entities--geo--country.csvand call this tibbleg_c. Letg_cbe your main tibble in thefollowing, i.e. add variables to this tibble.

6. How many countries are there now? The functionsunique()andlength()might be of some help.

## [1] 2476. How many countries are there now in each continent?## # A tibble: 5 x 2## # Groups:   continent [5]##   continent numbe
